### 2021-07-04 rad-icfp-2021/correctness.tex
writing a bit in correctness

\begin{definition}[$\ConcatS$]
Let $\ConcatS$ the syntactic Cartesian concategory whose types are those of Source and 
with primitives given by $op1: \reals \to \reals$, $op2: \reals,\reals \to \reals$ $map2_{x,y.e}$
and $reduce_{x,y.e1;e2}$.
\MH{actually I just need projection and a representing object for pairs, it might be weaker than Cartesian?}
\end{definition}

One may notice that the syntax of $\ConcatS$ is somewhere in between the syntax of Source and of Source UNF.
We can interpret Source UNF in $\ConcatS$ as follows.

\begin{tabular}{l c r}
   $\seml$!var!$_{T;i} \semr$ &=& \\
   $\seml$!op!$_{T;n} \semr$ &=& \\
   $\seml$!pair!$_{T;A\times B} \semr$ &=& \\
   $\seml$!proj!$_{T1;T2;T3} \semr$ &=& \\
   $\seml$!e!$\comp$!e!$\semr$  &=& \\
   $\seml$!e!$\pcomp$!e!$\semr$ &=& \\
   $\seml$!map2!$_{T;x,y.e}\semr$  &=& \\
   $\seml$!reduce!$_{T;x,y.e;e}\semr$  &=& \\
\end{tabular}

@@

\begin{definition}[$\ConcatT$]
Let $\ConcatT$ be the syntactic Cartesian concategory whose types are those of Target and 
with primitives given by $op1: \reals \to \reals$, $op2: \reals,\reals \to \reals$ $map2_{x,y.e}$, 
$reduce_{x,y.e1;e2}$, TODO
\MH{not too sure, should I say what a Cartesian concat is?}
\end{definition}

We can interpret Target UNF in $\ConcatT$ as follows.

\begin{tabular}{l c r}
    $\seml$!var!$_{T;i} \semr$ &=& \\
    $\seml$!op!$_{T;n} \semr$ &=& \\
    $\seml$!pair!$_{T;A\times B} \semr$ &=& \\
    $\seml$!proj!$_{T1;T2;T3} \semr$ &=& \\
    $\seml$!e!$\comp$!e!$\semr$  &=& \\
    $\seml$!e!$\pcomp$!e!$\semr$ &=& \\
    $\seml$!map2!$_{T;x,y.e}\semr$  &=& \\
    $\seml$!reduce!$_{T;x,y.e;e}\semr$  &=& \\
 \end{tabular}
\MH{Do I need any kind of proposition saying that this makes sense?
Might need to define on types as well to be clearer: It's an identity on type functor...}

@@

\begin{definition}[Mutlicat from concat]
    TODO
\end{definition}

>>>>

\begin{definition}[$\ConcatS$]
Let $\ConcatS$ the syntactic Cartesian concategory whose types are those of Source and 
with primitives given by $op1: \reals \to \reals$, $op2: \reals,\reals \to \reals$ $map2_{x,y.e}$
and $reduce_{x,y.e1;e2}$.
\MH{actually I just need projection and a representing object for pairs, it might be weaker than Cartesian? edit: I think I need Cartesian.}
\end{definition}

One may notice that the syntax of $\ConcatS$ is somewhere in between the syntax of Source and of Source UNF.

\begin{notation}[Morphisms in a Cartesian concategory]
    TODO: projection, unique map, $\concatcomp$, swap, pair, id, ...
\end{notation}

We can interpret Source UNF in $\ConcatS$ as follows.

\begin{tabular}{l c l}
   $\seml$!var!$_{T;i} \semr$ &=& $<id_\Gamma,\pi_i>$ \\
   $\seml$!op!$_{T;n} \semr$ &=& $id_\Gamma\concatcomp op_n$\\
   $\seml$!pair!$_{T;A\times B} \semr$ &=& $pair_{T;A\times B}$ \\
   $\seml$!proj!$_{T1;T2;T3} \semr$ &=& $id_{T1}\concatcomp 1_{T2}\concatcomp id_{T3}$\\
   $\seml$!e1!$\comp$!e2!$\semr$  &=& $\seml$!e1!$\semr \comp \seml$!e2!$\semr$ \\
   $\seml$!e1!$\pcomp$!e2!$\semr$ &=& $\seml$!e1!$\semr \comp (\seml$!e2!$\semr\concatcomp id )\comp swap$ \\
   $\seml$!map2!$_{T;x,y.e}\semr$  &=& $id_\Gamma\concatcomp map2_{x,y.e}$ \\
   $\seml$!reduce!$_{T;x,y.e;e}\semr$ &=& $id_\Gamma\concatcomp reduce_{x,y.e1;e2}$ \\
\end{tabular}

@@

\begin{definition}[$\ConcatT$]
Let $\ConcatT$ be the syntactic Cartesian concategory whose types are those of Target and 
with primitives given by 
$op1: \reals \to \reals$, 
$op2: \reals,\reals \to \reals$, 
$map2_{x,y.e}: \Array{\reals},\Array{\reals}\to \Array{\reals}$, 
$reduce_{x,y.e1;e2}: \Array{\reals} \to \Array{\reals}$, 
$J^Top1: \reals \to \reals$, 
$J^Top2: \reals \to \reals, \reals$, 
$J^Tmap2_{x,y.e}: \Array{\reals} \to \Array{\reals}, \Array{\reals}$, 
$J^Treduce_{x,y.e1;e2}: \Array{\reals} \to \Array{\reals}$, 
\MH{not too sure, should I say what a Cartesian concat is? do I need $J^Tproj$?}
\end{definition}

We can interpret Target UNF in $\ConcatT$ as follows. 
The part common with Source UNF is interpreted in the same way as for Source UNF.

\MH{I think need to explain here the (co)monoid structure induced by $D$}

\begin{tabular}{l c l}
    $\seml$!J!$^T$!var!$_{T;i} \semr$ &=& TODO \\
    $\seml$!J!$^T$!op!$_{T;n} \semr$ &=&  \\
    $\seml$!J!$^T$!pair!$_{T;A\times B} \semr$ &=& \\
    $\seml$!J!$^T$!proj!$_{T1;T2;T3} \semr$ &=& \\
    $\seml$!J!$^T$!map2!$_{T;x,y.e}\semr$  &=& \\
    $\seml$!J!$^T$!reduce!$_{T;x,y.e;e}\semr$  &=& \\
    $\seml$!<e1, e2>!$\semr$  &=& !<!$\seml$!e1!$\semr$, $\seml$!e2!$\semr$!>! \\
    $\seml$!e1!$\icomp$!e2!$\semr$ &=&  \\
 \end{tabular}
\MH{Do I need any kind of proposition saying that this makes sense?
Might need to define on types as well to be clearer: It's an identity on types functor...}

@@

\begin{definition}[Mutlicat from concat]
    A multicategory $\catC$ naturally defines a concategory with the same objects as $\catC$ and
    with morphisms $A\to [B1,...,Bn]$ being $n$ morphisms $A\to Bi$ of $\catC$. 
\end{definition}
